Latent Variable Clustering for Classification of Events in the AT-TPC

### 2020-06-01 doc/Manuscript/article.tex

\section{Machine Learning Methods}

\begin{itemize}
    \item Reiterate the aim of unsupervised  clustering of events.
    \item Challenges from a machine learning perspective. 
    \begin{itemize}
        \item Supervised vs. Unsupervised learning
        \item Define Classifcation and Clustering 
        \item Define latent space (refer)
        \item Traditional unupervised - distances in high dimensional spaces etc. 
    \end{itemize}
    \item Digression here to explain some ML concepts? Link back to Conv part of Michelles paper? 
    \item Opportunities presented by: 
    \begin{itemize}
        \item Transfer learning (train on VGG use on AT-TPC)
        \item Compression is understanding (leverage autoencoders) 
    \end{itemize}
    \item Building on Kuchera et. al we investigate the VGG16 networks application. 
    \item Novel contribution by applying clustering autoencoder networks. 
\end{itemize}

@@

\begin{figure}
\centering
	\includegraphics[width=\textwidth]{custom_work/Simulatedvgg_conf_mat.pdf} 
	\caption[Pre-trained network - confusion matrices]{Confusion matrix for the K-means clustering of simulated AT-TPC events. The true labels indicate samples belonging to the p (proton), or the carbon (C) class}\label{fig:clster_confmat}
\end{figure}

\begin{figure}
\centering
	\includegraphics[width=\textwidth]{custom_work/Filteredvgg_conf_mat.pdf}
	\caption[Pre-trained network - confusion matrices]{Confusion matrix for the K-means clustering of filtered AT-TPC events. The true labels indicate samples belonging to the p (proton), carbon (C), or other classes. }\label{fig:clster_confmat}
\end{figure}

\begin{figure}
	\includegraphics[width=\textwidth]{custom_work/Filteredvgg_conf_mat.pdf}
\caption[Pre-trained network - confusion matrices]{Confusion matrix for the K-means clustering of raw AT-TPC events. The true labels indicate samples belonging to the p (proton), carbon (C), or other classes. }\label{fig:clster_confmat}
\end{figure}

>>>>

\begin{itemize}
    \item Reiterate the aim of unsupervised  clustering of events.
    \item Challenges from a machine learning perspective. 
    \begin{itemize}
        \item Supervised vs. Unsupervised learning
        \item Define Classification and Clustering 
        \item Define latent space (refer)
        \item Traditional unsupervised - distances in high dimensional spaces etc. 
    \end{itemize}
    \item Digression here to explain some ML concepts? Link back to Conv part of Michelles paper? 
    \item Opportunities presented by: 
    \begin{itemize}
        \item Transfer learning (train on VGG use on AT-TPC)
        \item Compression is understanding (leverage autoencoders) 
    \end{itemize}
    \item Building on Kuchera et. al we investigate the VGG16 networks application. 
    \item Novel contribution by applying clustering autoencoder networks. 
\end{itemize}

@@

\begin{figure}
\centering
	\includegraphics[width=\textwidth]{custom_work/Simulatedvgg_conf_mat.pdf} 
	\caption[Pre-trained network - confusion matrices]{Confusion matrix for the K-means clustering of simulated AT-TPC events. The true labels indicate samples belonging to the p (proton), or the carbon (C) class}\label{fig:clster_confmat_sim}
\end{figure}

\begin{figure}
\centering
	\includegraphics[width=\textwidth]{custom_work/Filteredvgg_conf_mat.pdf}
	\caption[Pre-trained network - confusion matrices]{Confusion matrix for the K-means clustering of filtered AT-TPC events. The true labels indicate samples belonging to the p (proton), carbon (C), or other classes. }\label{fig:clster_confmati_filt}
\end{figure}

\begin{figure}
	\includegraphics[width=\textwidth]{custom_work/Rawvgg_conf_mat.pdf}
\caption[Pre-trained network - confusion matrices]{Confusion matrix for the K-means clustering of raw AT-TPC events. The true labels indicate samples belonging to the p (proton), carbon (C), or other classes. }\label{fig:clster_confmati_raw}
\end{figure}
